---
title: "Downloads"
---

```{r}
#| echo: false
source("scripts/site_helpers.R")
meta <- read_meta()
```

All data is hosted on this site and mirrored in the
[GitHub repository](https://github.com/slub/tu9-openalex) — outputs under
[`data/`](https://github.com/slub/tu9-openalex/tree/main/data), the pipeline
input under
[`data-raw/`](https://github.com/slub/tu9-openalex/tree/main/data-raw).

## Files

Alliance-wide views:

- [`metrics.csv`](metrics.csv) — one row per university per snapshot: the
  corresponding-author OA headline (period `ca_works_period` / `ca_oa_share_period`
  and the reference-year `ca_*_ref`) plus context indicators (works, citations,
  h-index, i10-index, 2-year mean citedness). Works come under three lenses:
  `works_count` (institution only, XPAC excluded), `works_count_incl_xpac` (same
  institution, XPAC included) and `works_count_lineage_incl_xpac` (additionally
  its OpenAlex child institutions — the figure openalex.org links to)
- [`counts_by_year.csv`](counts_by_year.csv) — works and citations by
  publication year, for the most recent snapshot
- [`ca_oa_by_year.csv`](ca_oa_by_year.csv) — **corresponding-author** OA share
  by publication year (`ca_works`, `ca_oa_works`, `ca_oa_share`) plus DOAJ-listed
  journal counts (`ca_doaj_works`, `ca_doaj_share`)
- [`ca_oa_status.csv`](ca_oa_status.csv) — corresponding-author OA-status split
  (gold/hybrid/green/bronze/diamond/closed) for the reference year
- [`consolidated_ca_oa_by_year.csv`](consolidated_ca_oa_by_year.csv) —
  **Leiden-consolidated** CA OA share by year: each TU9 university counted
  together with its weight-1 `component` affiliates (e.g. its university hospital)
- [`leiden_core_ca_oa_by_year.csv`](leiden_core_ca_oa_by_year.csv) —
  **Core-source-filtered** CA OA share by year: same Leiden-consolidated member
  set, restricted to CWTS Core sources via
  `primary_location.source.is_core:true`

Per institution (metric history + yearly counts + OA views, plus every raw
snapshot):

```{r}
#| echo: false
#| output: asis
for (x in meta$institutions) {
  cat(sprintf(
    "- `institutions/%s/` — [metrics.csv](institutions/%s/metrics.csv) · [counts_by_year.csv](institutions/%s/counts_by_year.csv) · [ca_oa_by_year.csv](institutions/%s/ca_oa_by_year.csv) · [ca_oa_status.csv](institutions/%s/ca_oa_status.csv) · [consolidated_ca_oa_by_year.csv](institutions/%s/consolidated_ca_oa_by_year.csv) · [leiden_core_ca_oa_by_year.csv](institutions/%s/leiden_core_ca_oa_by_year.csv)\n",
    x$slug, x$slug, x$slug, x$slug, x$slug, x$slug, x$slug))
}
```

Each institution's raw OpenAlex entity is archived per snapshot under
`institutions/<slug>/snapshots/<date>.json`.

Pipeline inputs:

- [`institutions.csv`](institutions.csv) — the tracked institutions with their
  OpenAlex and ROR IDs
- [`leiden_affiliations.csv`](leiden_affiliations.csv) — the TU9 slice of the
  Leiden Ranking institution-consolidation mapping (which affiliated
  organisations are counted into each university, with relation type and weight)

Other:

- [`meta.json`](meta.json) — summary counts and last-updated date
- [`DATA-LICENSE`](DATA-LICENSE) — the data licence (CC0 1.0)
