---
title: "Downloads"
---

```{r}
#| echo: false
source("scripts/site_helpers.R")
meta <- read_meta()
```

All data is hosted on this site and mirrored in the
[GitHub repository](https://github.com/slub/tu9-openalex) — outputs under
[`data/`](https://github.com/slub/tu9-openalex/tree/main/data), the pipeline
input under
[`data-raw/`](https://github.com/slub/tu9-openalex/tree/main/data-raw).

## Files

Alliance-wide views:

- [`metrics.csv`](metrics.csv) — one row per institution per snapshot (works,
  citations, h-index, i10-index, 2-year mean citedness)
- [`counts_by_year.csv`](counts_by_year.csv) — works and citations by
  publication year, for the most recent snapshot

Per institution (metric history + yearly counts, plus every raw snapshot):

```{r}
#| echo: false
#| output: asis
for (x in meta$institutions) {
  cat(sprintf(
    "- `institutions/%s/` — [metrics.csv](institutions/%s/metrics.csv) · [counts_by_year.csv](institutions/%s/counts_by_year.csv)\n",
    x$slug, x$slug, x$slug))
}
```

Each institution's raw OpenAlex entity is archived per snapshot under
`institutions/<slug>/snapshots/<date>.json`.

Pipeline input:

- [`institutions.csv`](institutions.csv) — the tracked institutions with their
  OpenAlex and ROR IDs

Other:

- [`meta.json`](meta.json) — summary counts and last-updated date
- [`DATA-LICENSE`](DATA-LICENSE) — the data licence (CC0 1.0)
