---
title: "TU9 OpenAlex Metrics"
---

```{r}
#| echo: false
source("scripts/site_helpers.R")
meta <- read_meta()
```

Aggregated bibliometric indicators for the [TU9](https://www.tu9.de/)
universities and closely related institutions, taken directly from their
[OpenAlex](https://openalex.org/) institution records and snapshotted over
time. Each figure — works, citations, h-index, works per year — is the value
OpenAlex already reports for the institution; this site records how those
values evolve.

The data is refreshed on a schedule and released under CC0. See
[Background](background.qmd) for how institutions are selected and what each
metric means, and [Downloads](downloads.qmd) for the raw files.

```{r}
#| echo: false
#| output: asis
cat(sprintf(
  "*Last updated: **%s**. Covers **%s** institutions across **%s** snapshot(s).*\n",
  meta$updated, meta$n_institutions, meta$n_snapshots))
```

## Institutions

```{r}
#| echo: false
institutions_table(meta$institutions)
```

Figures reflect the most recent snapshot. Select an institution for its metric
history and a works-by-year breakdown.
