---
title: "TU9 Open Access Monitoring with OpenAlex"
---

```{r}
#| echo: false
source("scripts/site_helpers.R")
meta <- read_meta()
```

Open-access monitoring for the [TU9](https://www.tu9.de/) universities, built from [OpenAlex](https://openalex.org/) and snapshotted over time.
The headline is each university's open-access share on the *corresponding-author* lens — the basis also used for [OpenAPC](https://openapc.net/) and transformative-agreement reporting.

Refreshed on a schedule and released under CC0.

```{r}
#| echo: false
#| output: asis
cat(sprintf(
  "*Last updated: **%s**. Covering **%s** OpenAlex institution entities incl. consolidated components over **%s** %s. Figures span corresponding-author works published **%s–%s**.*\n",
  meta$updated, meta$n_entities, meta$n_snapshots,
  if (meta$n_snapshots == 1) "snapshot" else "snapshots",
  meta$oa_period_start, meta$oa_period_end))
```

## Coverage of the alliance

```{r}
#| echo: false
alliance_summary_table(meta)
```

Each reading deduplicates corresponding-author works across all nine universities, so a work associated with multiple members is counted once. Distinct CA works is the resulting alliance-wide count; CA OA share is the corresponding direct ratio, not an average of university shares.

Explore further: **[Institutions](institutions/index.qmd)** — results by university · **[Background](background.qmd)** — methodology, sources, and definitions · **[Downloads](downloads.qmd)** — the raw data files.
