---
title: "TU9 Open Access Monitoring with OpenAlex"
---

```{r}
#| echo: false
source("scripts/site_helpers.R")
meta <- read_meta()
```

Open-access monitoring for the [TU9](https://www.tu9.de/) universities, built from [OpenAlex](https://openalex.org/) and snapshotted over time.
The headline is the open-access share on the corresponding-author lens — the fraction of a university's corresponding-author output that is open access.
That is the view which matches [OpenAPC](https://openapc.net/) and transformative-agreement accounting, and the one relevant to OA monitoring.

Each university is shown three ways: as the single OpenAlex institution, grouped with its affiliated organisations the way the [Leiden Ranking](https://open.leidenranking.com/) defines (e.g. with its university hospital), and that same Leiden member set restricted to CWTS Core sources via `primary_location.source.is_core:true`.
See [Background](background.qmd) for method and sources and [Downloads](downloads.qmd) for the raw files.

Refreshed on a schedule and released under CC0.

```{r}
#| echo: false
#| output: asis
cat(sprintf(
  "*Last updated: **%s**. Covering **%s** OpenAlex institution entities incl. consolidated components over **%s** %s. Figures span corresponding-author works published **%s–%s**.*\n",
  meta$updated, meta$n_entities, meta$n_snapshots,
  if (meta$n_snapshots == 1) "snapshot" else "snapshots",
  meta$oa_period_start, meta$oa_period_end))
```

## Coverage of the alliance

```{r}
#| echo: false
alliance_summary_table(meta)
```


All three readings cover the same nine universities, so the totals are directly comparable.
Consolidating adds the weight-1 Leiden `component` affiliates and can therefore only raise a university's count; three universities have no such affiliates and consolidate to themselves.
Core sources uses the consolidated member set with publications restricted to CWTS Core sources, so it is always the smallest of the three.

The [Institutions](institutions/index.qmd) page breaks the same three readings down per university.
