---
title: "TU9 OpenAlex Metrics"
---

```{r}
#| echo: false
source("scripts/site_helpers.R")
meta <- read_meta()
```

Open-access monitoring for the [TU9](https://www.tu9.de/) universities,
built from [OpenAlex](https://openalex.org/) and snapshotted over time. The
headline is the **open-access share on the corresponding-author lens**
(`corresponding_institution_ids`) — the fraction of a university's
corresponding-author output that is open access. That is the view which matches
[OpenAPC](https://openapc.net/) and transformative-agreement accounting, and the
one relevant to OA monitoring.

Each university is shown three ways: as the single OpenAlex institution,
grouped with its affiliated organisations the way the
[Leiden Ranking](https://open.leidenranking.com/) defines (e.g. with its
university hospital), and that same Leiden member set restricted to CWTS Core
sources via `primary_location.source.is_core:true`. See [Background](background.qmd)
for method and sources and [Downloads](downloads.qmd) for the raw files.
Refreshed on a schedule and released under CC0.

```{r}
#| echo: false
#| output: asis
cat(sprintf(
  "*Last updated: **%s**. Covering **%s** OpenAlex institution entities incl. consolidated components over **%s** %s. Figures span corresponding-author works published **%s–%s**.*\n",
  meta$updated, meta$n_entities, meta$n_snapshots,
  if (meta$n_snapshots == 1) "snapshot" else "snapshots",
  meta$oa_period_start, meta$oa_period_end))
```

## Coverage of the alliance

```{r}
#| echo: false
alliance_summary_table(meta)
```

Consolidated totals include only the six universities that have weight-1 Leiden
`component` affiliates; the other three have no consolidated row because the
single-institution and consolidated member sets would be identical.

The [Institutions](institutions/index.qmd) page breaks the same three readings
down per university.
