---
title: "TU9 OpenAlex Metrics"
---

```{r}
#| echo: false
source("scripts/site_helpers.R")
meta <- read_meta()
```

Open-access monitoring for the [TU9](https://www.tu9.de/) universities,
built from [OpenAlex](https://openalex.org/) and snapshotted over time. The
headline is the **open-access share on the corresponding-author lens**
(`corresponding_institution_ids`) — the fraction of a university's
corresponding-author output that is open access. That is the view which matches
[OpenAPC](https://openapc.net/) and transformative-agreement accounting, and the
one relevant to OA monitoring.

Each university is shown three ways: as the single OpenAlex institution,
grouped with its affiliated organisations the way the
[Leiden Ranking](https://open.leidenranking.com/) defines (e.g. with its
university hospital), and that same Leiden member set restricted to CWTS Core
sources via `primary_location.source.is_core:true`. See [Background](background.qmd)
for method and sources and [Downloads](downloads.qmd) for the raw files.
Refreshed on a schedule and released under CC0.

```{r}
#| echo: false
#| output: asis
cat(sprintf(
  "*Last updated: **%s**. **%s** OpenAlex institution entities incl. consolidated components, **%s** snapshot(s). Figures cover corresponding-author works published **%s–%s**.*\n",
  meta$updated, meta$n_entities, meta$n_snapshots, meta$oa_period_start, meta$oa_period_end))
```

## Institutions

```{r}
#| echo: false
institutions_table(meta)
```

Each university is shown three ways, each with its own corresponding-author
**CA works** count (works published in the period whose corresponding author is
at the institution) and the **CA OA share** among them:

- **Single institution (ROR/OpenAlex)** — the one OpenAlex institution
  identified by the university's [ROR](https://ror.org/) id.
- **Consolidated (OpenAlex/Leiden)** — the university grouped with its Leiden
  `component` affiliates (e.g. its university hospital). Blank where a university
  has no components, so the two readings would be identical.
- **Core sources (Leiden/Core)** — the same Leiden-consolidated member set,
  additionally restricted to sources on the CWTS Core sources allow-list
  (`primary_location.source.is_core:true`). Populated for all nine universities,
  because the source filter changes the publication universe even where there are
  no component affiliates.

Select a university for its OA share by year, OA-status composition, and snapshot
history.
