---
title: "Institutions"
---

```{r}
#| echo: false
source("scripts/site_helpers.R")
meta <- read_meta()
```

Figures cover corresponding-author works published
**`r meta$oa_period_start`–`r meta$oa_period_end`**, per university. The
[home page](../index.qmd) totals the same three readings across the alliance.

```{r}
#| echo: false
institutions_table(meta, path_prefix = "")
```

Each university is shown three ways, each with its own corresponding-author
**CA works** count (works published in the period whose corresponding author is
at the institution) and the **CA OA share** among them:

- **Single institution (ROR/OpenAlex)** — the one OpenAlex institution
  identified by the university's [ROR](https://ror.org/) id.
- **Consolidated (OpenAlex/Leiden)** — the university grouped with its Leiden
  `component` affiliates (e.g. its university hospital). Blank where a university
  has no components, so the two readings would be identical.
- **Core sources (Leiden/Core)** — the same Leiden-consolidated member set,
  additionally restricted to sources on the CWTS Core sources allow-list
  (`primary_location.source.is_core:true`). Populated for all nine universities,
  because the source filter changes the publication universe even where there are
  no component affiliates.

Select a university for its OA share by year, OA-status composition, and snapshot
history.
