---
title: "Institutions"
---

```{r}
#| echo: false
source("scripts/site_helpers.R")
meta <- read_meta()
```

Figures cover corresponding-author works published `r meta$oa_period_start`–`r meta$oa_period_end`, per university.
The [home page](../index.qmd) totals the same three readings across the alliance.

```{r}
#| echo: false
institutions_table(meta, path_prefix = "")
```

Each university is shown three ways, each with its own CA works count (works published in the period whose corresponding author is at the institution) and the CA OA share among them:

- **Single institution (ROR/OpenAlex)** — the one OpenAlex institution identified by the university's [ROR](https://ror.org/) id.
- **Consolidated (OpenAlex/Leiden)** — the university grouped with its Leiden `component` affiliates (e.g. its university hospital). A university without components consolidates to itself.
- **Core sources (Leiden/Core)** — the same Leiden-consolidated member set, additionally restricted to works whose primary venue is a source on the CWTS Core sources list.

Select a university for its OA share by year, OA-status composition, and snapshot history.
